---
title: "Exercises Class 1"
author: "Tim Nieuwenhuis"
date: "11/12/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\#Exercises 1

## 1. Power, square toots, logs

```{r}
#Single number
x = 4
##Power
x**2
x^2
## Square root
sqrt(x)
## Log and natural Log
log10(x)
log(x)


## Generate a random vector
x=c(1,2.4,-5)


## See how it works vectorized
##Power
x**2
x^2
## Square root
sqrt(x)
## Log and natural Log
log10(x)
log(x)

```

## 2. What happens when you apply arithmetic operations to logical values (e.g., TRUE + TRUE, or TRUE+ FALSE) What can you conclude about how logical values are stored in R?

```{r}
TRUE + TRUE
TRUE + FALSE
## TRUE is coded as 1 and FALSE is coded as 0
```

## 3. What happens when you compare a numeric value to a string (e.g., "a" \> 1) What is happening to the numeric variable in this comparison?}

```{r}
"a" > 1
"a" > 100
"a" > Inf

```

Seems to be treated higher than all numerics except infinity
